### 2018-08-02 Writing/best_practices_version.tex
Backup best practices version

\noindent (Keywords: disparity)\\

@@

%---------------------------------------------
%
%       INTRODUCTION
%
%---------------------------------------------
\section{Introduction}

>>>>

\noindent (Keywords: disparity, multidimensionality, palaeobiology, ecology)\\

@@

%---------------------------------------------
%
%       NEW PLAN
%
%---------------------------------------------

% Intro
% IN -> history
%     -Disparity or diversity?
%     Is disparity just diversity? No.
% OU -> Disparity can be many things

% -Diversity of disparities
% IN -> There are many different disparity
%     -Ecological
%     -Functional
%     -Phylogenetic

%     However, do these disparities represent anything more than the disparity of those traits rather than the disparity of the thing?
%     Maybe. Disparity traits need to be carefully selected in order to properly reflect the thing. Disparity is only a proxy to describe the pattern and does not necesserly make conclusions on the process (but see disparity pattern vs disparity process)

% OU -> But in general, disparity is a disparity of traits (Best practice: by the way, it's good to have a clear selection of the traits)

% - Trait disparity
% IN -> If it's just traits, can all of the traits be used?
%     Which traits should be collected?
%     Do discrete and continuous trait reflect the same thing? If yes, what does that imply?
%     Can disparity analysis work with any kind of trait?
%     Does the part represent the whole?
% OU -> And how do these traits need to be analysed?

% - Disparity is multidimensional
% IN -> Disparity is multidimensional by essence
%     Do we need trait reduction (ordination) or can we do without?
%     What do we measure from these multidimensional spaces?
% OU -> And how do we test these things?

% - Disparity hypothesis
% IN -> So how do we go for testing hypotheses in disparity?
%     What are our null expectations?
%     How can we analyse it through time?

% - A disparity future
% IN -> The definition of disparity and its uses have broadened since the early disparity start.
%     What can we get from other fields to make disparity better
%     But also what can we bring to other fields (discussions with Abigail)

%---------------------------------------------
%
%       INTRODUCTION
%
%---------------------------------------------

\section{Introduction}

%Historical blurb
Variation in the shape, form and function of organisms often follows discrete patterns rather than continuous gradients.
These patterns can be pictured as multidimensional spaces encompassing all the possible forms an organism can take, and where each individual region of this space is the result of a discrete combination of many variables.
One commonly used approach to analyse these discrete patterns, and to understand the processes that lead to them, is to analyse the disparity of the morphological characteristics of the group, often referred to as ``morphological disparity analysis''.

\section{Introduction}
% IN -> history
\subsection{Is disparity equivalent to diversity?}
% OU -> Disparity can be many things

\section{A diversity of disparities}
% IN -> There are many different disparity

\subsubsection{Morphological disparity}
\subsubsection{Functional disparity}
\subsubsection{Ecological disparity}
\subsubsection{Phylogenetic disparity}

%However, do these disparities represent anything more than the disparity of those traits rather than the disparity of the thing?

%Maybe. Disparity traits need to be carefully selected in order to properly reflect the thing. Disparity is only a proxy to describe the pattern and does not necesserly make conclusions on the process (but see disparity pattern vs disparity process)

% OU -> But in general, disparity is a disparity of traits (Best practice: by the way, it's good to have a clear selection of the traits)

\section{Trait disparity}
% IN -> If it's just traits, can all of the traits be used?
%     Which traits should be collected?

\subsection{Are different traits equivalent?}
%     Can disparity analysis work with any kind of trait?

\subsection{Are different dataset equivalent?}
%     Do discrete and continuous trait reflect the same thing? If yes, what does that imply?

\subsection{Does the part represent the whole?}
%     Does the part represent the whole?

% OU -> And how do these traits need to be analysed?

\section{Disparity is multidimensional}
% IN -> Disparity is multidimensional by essence
%     Do we need trait reduction (ordination) or can we do without?
%     What do we measure from these multidimensional spaces?
% OU -> And how do we test these things?

\section{Disparity hypotheses}
% IN -> So how do we go for testing hypotheses in disparity?
%     What are our null expectations?
%     How can we analyse it through time?

\section{A disparate future?}
% IN -> The definition of disparity and its uses have broadened since the early disparity start.
%     What can we get from other fields to make disparity better
%     But also what can we bring to other fields (discussions with Abigail)

%i) the relationship between diversity and disparity
1 - What is the relation between disparity and diversity? They are decoupled
Disparity can be used as a parallel metric for biodiversity: species diversity (or alpha or beta diversity) aim to describe the number of population as reproductive isolates.
On the other hand, disparity aims to describe the number of traits combination (e.g. shapes, ecologies, etc.).
They can sometimes approximate the same thing (i.e. really low diversity can sometimes mean really low disparity) but have often been showed as decouple [CITES].
A classic example is among mammals, really specious groups like Rodents display low morphological disparity (at least at the superficial scale) but high diversity. Conversely, carnivorans display a relatively lower diversity but a much higher morphological disparity.

%ii) the ensuing ideas on evolvability
2 - Disparity can be linked to evolvability? A morphological disparate group is likely to occupy more niches (but see the debate for the link between traits and ecological niches [CITES]) and more likely to be the result from character displacement and/or competition.
Also, more disparate groups are more likely to lead to disparate radiations as different ecological strategies get explored.

%iii) parallels with the evolution of gene regulatory evolution, and the extension of this approach to studying the evolution of ecological and functional disparity
3.1- Ecological disparity: promising tool at a macro-evolutionary scales (but maybe less at micro-evolutionary scales). E.g. the concept of ecological guilds can be distinguished in the fossil record (carnivoran guild etc.) but it might be more difficult to grasp at a micro-scale level (CITE plant trait/niche papers).
3.2- Functional disparity: seems to work at any scale and can be used to test convergence (species with similar trait combination can have similar functions) or the link between form and function (Diaz paper). However, the link between trait and function can sometimes be hard to grasp since traits can be linked to multiple functions and multiple functions can be linked to a single trait.

%do continuous and categorical characters capture the same disparity?
%Does a part represent the whole?
%Do paleontological/ ecological/ functional disparities represent anything more than a disparity of those characters, rather than disparity of morphology/ ecology/ function?
%Time slicing?
%Character equivalence?
%Is ordination meaningful?

% It is inevitable that this manuscript is going to be a shit sandwich but I think it is currently an open sandwich and needs an introduction that reviews not only what disparity is, from whence it came and whither it goes, we also need to review what we have learned so far: (, (, ( of (iv) ecological and (v) functional disparity.

% I would follow this with a discussion of the problems that have emerged in study: do continuous and categorical characters capture the same disparity? Does a part represent the whole? Do paleontological/ ecological/ functional disparities represent anything more than a disparity of those characters, rather than disparity of morphology/ ecology/ function? Time slicing? Character equivalence? Is ordination meaningful?

% I think that I would make this discussion less abstract and use examples. We should also write this as though the prospective articles do not exist – because they don’t. What are the solutions? I think they usually involve forethought in place of playing with data and hoping some interesting but untestable phenomenon falls out. And, of course, follow with a prospect on what could be done in future….

% Most of it is there – it just needs jiggling about and editing a bit – as well as adding to.

% We were asked originally to write a review on this topic and so we’re pushing the envelope in writing about best practices. I’m comfortable with that, but we still need to achieve the basic expectation of a review – though I always prefer an insightful (more than the sum of its parts) review, rather than a piece of journalism.

% So in a round about way, yes, I think we do need to have a ‘what we have learned’ aspect to the manuscript.

\section{Introduction}
